### 2024-03-03 docs/projects/datavis/observable/index.qmd
Observable - rerendered

::: {.sourceClojure}
```clojure
(ns index
  (:require [codegen :refer [obs]]))
```
:::

# Observable examples

@@

We follow [a basic example]((https://quarto.org/docs/interactive/ojs/libraries.html#plot))
from Quarto's Observable docs.

>>>>

# Observable examples - DRAFT

::: {.sourceClojure}
```clojure
(ns index
  (:require [codegen :refer [obs]]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

@@

We follow [a basic example](https://quarto.org/docs/interactive/ojs/libraries.html#plot)
from Quarto's Observable docs.
